Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
sup

~\newline\textbf{III. Other DML Loss Functions}

Although the traditional triplet loss could reach the state-of-the-art
performance with an appropriate sampling strategy, many other DML loss
functions are proposed.
%
Adversarial trainig with other DML loss functions is unexplored.
%
New metric learning loss functions oriented for adversarial training is
also left for future study.

>>>>

~\newline\textbf{III. Other Loss Functions}

Adversarial trainig with DML loss functions other than triplet loss is
insufficiently explored.
%
New metric learning loss functions oriented for adversarial training are also
left for future study.
%
Besides, model collapse is an inevitable problem for adversarial training
with triplet loss, and it is unknown whether other loss functions could
mitigate this issue.
